% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\robustify\cftdotfill


%-----------------------------------------------------------
%Edit these values as you see fit

\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars


%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}


%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}
\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Cory Nance} \\
Visiting Assistant Professor at The Citadel \\
(email) cnance@citadel.edu\\
(office) (843) 953-1661\\
\end{tabular*}
\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item
	\ressubheading{Dakota State University}{Madison, SD}{Ph.D. in Cyber Operations}{2020}
\item
	\ressubheading{Georgia Southern University}{Statesboro, GA}{M.Sc. Computer Science}{2013}
\item
	\ressubheading{Coastal Carolina University}{Conway, SC}{B.Sc. Computer Science}{2010}


	
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}

\item {\bf Nance, C.} (2019). Towards a Virtual Machine Introspection Based Multi-Service, Multi-Architecture, High-Interaction Honeypot for IoT Devices. In Proceedings of the Southern Association for Information Systems Conference.

\item Frank, C., {\bf Nance, C.}, Jarocki, S., Pauli, W. E. (2018). Protecting IoT from Mirai botnets; IoT
device hardening. Journal of Information Systems Applied Research, 11(2) pp 33-44.
http://jisar.org/2018-11/ ISSN: 1946-1836. (A preliminary version appears in The Proceedings of
CONISAR 2017)

\item French, J. H., Murphy, M., {\bf Nance, C.}, \& Cox, C. (2017). Diversifying Computing Degree
Programs to Improve Student Retention. Journal of Computing Sciences in Colleges, 33(2), 237-244.

\item Frank, C., {\bf Nance, C.}, Jarocki, S., \& Pauli, W. E. (2017). Protecting IoT from Mirai botnets; IoT device hardening. Proceedings of the Conference on Information Systems Applied Research

\item {\bf Nance, C.}, Losser, T., Iype, R., \& Harmon, G. (2013). NoSQL vs RDBMS - Why There is Room for Both. In Proceedings of the Southern Association for Information Systems Conference.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}

\item {\bf Nance, C.} (2020, May 6). A VMI Honeypot for IoT Device Emulation. Presented at Charleston InfoSec Group: Talks on Tap in Charleston, SC.

\item {\bf Nance, C.} (2018, November 14). Protecting Personal Information:
Passphrases, Passwords, Encryption, MFA, and Physical Security. Presented at Information Security Awareness Week in Coastal Carolina University, Conway, SC.
\item {\bf Nance, C.} (2018, November 8). Demystifiying the Cloud. Presented at One Talk, One Time in Coastal Carolina University, Conway, SC.
\item Auger, G., Flaagan, T., \& {\bf Nance, C.} (2017, November 11). RevEng All the IoTs. Presented at BSides Charleston in College of Charleston School of Business, Charleston, SC.
\item {\bf Nance, C.} (2017, October 24). Protecting IoT from Mirai botnets; IoT device hardening. Presented at One Talk, One Time in Coastal Carolina University, Conway, SC.
\end{enumerate}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Poster Presentations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{enumerate}
    
\item Frank, C., {\bf Nance, C.}, Jarocki, S., \& Pauli, W. (2018). Defensive Techniques for IoT Botnets. AFCEA Cyber Education, Research, and Training Symposium.

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Grants}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\vspace{-2pt}
	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
        \multicolumn{2}{c}{CCU Professional Enhancement Grant (\$2,240) \cftdotfill{\cftdotsep} 2019}\\
	        \multicolumn{2}{c}{CCU Online Learning Incentive Grant (\$5,400) \cftdotfill{\cftdotsep} 2017-2018}\\
		\multicolumn{2}{c}{Google Cloud Platform Education Grant (\$5,500) \cftdotfill{\cftdotsep} 2017}\\
        \multicolumn{2}{c}{CCU Online Learning Incentive Grant (\$8,400) \cftdotfill{\cftdotsep} 2016-2017}\\
		\vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Service}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\vspace{-2pt}
	\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
	\multicolumn{2}{c}{Faculty Advisor - Cybersecurity Club \cftdotfill{\cftdotsep} 2019}\\
	 \multicolumn{2}{c}{Scholarship Committee Member \cftdotfill{\cftdotsep} 2018 - 2019}\\
		 \multicolumn{2}{c}{Faculty Advisor - ACM Student Chapter \cftdotfill{\cftdotsep} 2017 - 2019}\\
	            \multicolumn{2}{c}{IS Curriculum Committee Member \cftdotfill{\cftdotsep} 2014 - 2019}\\
             \multicolumn{2}{c}{IT Curriculum Committee Member \cftdotfill{\cftdotsep} 2014 - 2019}\\
             \multicolumn{2}{c}{Search Committee Member: Assistant Professor of IT\cftdotfill{\cftdotsep} 2016 - 2017}\\
              \multicolumn{2}{c}{Search Committee Member: Lecturer of Computing Sciences \cftdotfill{\cftdotsep} 2015 - 2016}\\
        		\multicolumn{2}{c}{Search Committee Member: Assistant Professor of IT \cftdotfill{\cftdotsep} 2014}\\
          
           

		\vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Courses Taught}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item The Citadel
    \begin{itemize}
        \item CSCI 201: Introduction to Computer Science I
        \item CSCI 211: Introduction to Computer Science I Lab 
        \item CSCI 202: Introduction to Computer Science II
        \item CSCI 227: Principles and Practices of Cybersecurity
        \item CSCI 305: Computer Organization and Programming
    \end{itemize}

	\item Coastal Carolina University
	\begin{itemize}
	    \item CSCI 101: Introduction to the Internet and World Wide Web
	    \item CSCI 110: Enterprise Business Applications
		\item CSCI 130: Introduction to Computer Science
		\item CSCI 131L: Algorithmic Thinking
		\item CSCI 135: Introduction to Programming
		\item CSCI 140: Introduction to Algorithmic Design I
		\item CSCI 140L: Introduction to Algorithmic Design I Lab
		\item CSCI 145: Intermediate Programming
		\item CSCI 150: Introduction to Algorithmic Design II
		\item CSCI 150L: Introduction to Algorithmic Design II Lab
		\item CSCI 211: Computer Infrastructure
		\item CSCI 216: Linux Fundamentals I
		\item CSCI 385: Introduction to Information Systems Security
		\item CSCI 415: Windows Systems Administration
		\item CSCI 425: Database Design
		\item CSCI 495: IS Project and Capstone
	\end{itemize}
	\item Horry-Georgetown Technical College
	\begin{itemize}
		\item CPT 187: Object-Oriented Logic and Design
	\end{itemize}
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Awards}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}\begin{tabular*}{6.6in}{l@{\extracolsep{\fill}}r}
        \multicolumn{2}{c}{Outstanding Chauncey\textsc{\char13}s Service Excellence Champion (Finalist) \cftdotfill{\cftdotsep} 2018}\\
        \multicolumn{2}{c}{Chauncey\textsc{\char13}s Service Excellence Champion \cftdotfill{\cftdotsep} 2017}\\

		\vphantom{E}
\end{tabular*}
\end{center}\vspace*{-16pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Professional Development}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
\item 2020
\begin{itemize}
    \item Basis Technologies: Autopsy 8-Hour Online Training
\end{itemize}
	\item 2019
	\begin{itemize}
	    \item Open Information Security Foundation: Threat Hunting with Suricata
	    \item Using Best Practices to Update Your Online Learning Course
	    \item Personal Lecture Capture for Online/Hybrid Classes
	\end{itemize}
	\item 2018
	\begin{itemize}
	    \item BSides Charleston: A Crash-Course on Internal Network Penetration Testing
	    \item BSides Charleston: Container Hacking
	    \item Best Practices for Teaching Accelerated Courses
	    \item Working with Student Groups in Your Online Class
	\end{itemize}
	\item 2017
	\begin{itemize}
		\item Grand Idea Studio: Hands-on Hardware Hacking Training
		\item Integration of Accessible Assignments and Activities into your Online, Hybrid and Flex Classes
	\end{itemize}
	\item 2016
	\begin{itemize}
	    \item  Applying the Quality Assurance Inventory to Your Online Course
	    \item  Building a Framework for Your Distance Learning Moodle Course
	    \item  Transform Your Students From Passive to Active Learners
	    \item  Survey of Tech Tools for Distance Learning Instructors
	    \item  Using Mid-Semester Feedback to Improve Your Course
	    \item  Organizing Your Distance Learning Course
	    \item  Classroom Motivation and Management
	    \item  Creating a Distance Learning Syllabus
		\item  Active Learning to Enhance Lectures
	    \item  Integrating Instructional Technology
		\item  Make Your Lectures More Effective
		\item  Managing Your Online Workload
		\item  Interpreting Student Evaluations
		\item  Building an Inclusive Classroom
		\item  Classroom Instruction Methods
		\item  Course Design and Preparation
		\item  Creating Learning Guides
		\item  Developing a Course Plan
		\item  Assessment Strategies
	\end{itemize}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\resheading{Work Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}

\item
	\ressubheading{The Citadel: The Military College of South Carolina
}{Charleston, SC}{Visiting Assistant Professor}{August 2019 - current}
	\begin{itemize}
      \resitem{Academic Advisor}
      \item Faculty member of the Department of Cyber and Computer Sciences
	\end{itemize}
\item

\item
	\ressubheading{Coastal Carolina University}{Conway, SC}{Lecturer}{August 2014 - August 2019}
	\begin{itemize}
      \resitem{Academic Advisor}
      \item Faculty member of the Department of Computing Sciences 
	\end{itemize}
\item

\item
	\ressubheading{Horry-Georgetown Technical College}{Conway, SC}{Systems Administrator}{May 2013 - August 2014}
	\begin{itemize}
      \resitem{Provide college-wide and across all campuses, technical support and services in the operation and administration of enterprise-level servers and related infrastructure.}
      \item Install, configure, and operate a Windows and Linux server environment consisting of physical and virtual (VMware) servers, Storage Area Network (SAN), and related hardware/software.
      \item Monitor, troubleshoot, and maintain server hardware and storage products; and confer with vendors in diagnosing and correcting errors.
      \item Assist with maintaining application and support systems including, but not limited to, e-mail system (Exchange), spam filtering, database (SQL Server), user accounts (Active Directory), and domain name service (DNS).
      \item Assist with implementing the necessary controls, procedures, and best practices for maintaining information security of hardware, server resources, and systems.
      \item Assist with performing data backup and recovery procedures; and adhere to established retention schedule.
      \item Assist in researching new technologies and perform other related duties as may be assigned.
	\end{itemize}
\item


\item
	\ressubheading{Coastal Carolina University}{Conway, SC}{Teaching Associate}{August 2013 - May 2014}
	\begin{itemize}
		\resitem{Teaching undergraduate courses in Computer Science.}
	\end{itemize}
	
\item
	\ressubheading{Horry-Georgetown Technical College}{Conway, SC}{Adjunct Faculty}{January 2013 - May 2013}
	\begin{itemize}
		\resitem{Teaching object-oriented language and design (Java).}
	\end{itemize}
	
\item
	\ressubheading{Horry-Georgetown Technical College}{Conway, SC}{Applications Analyst}{November 2011 - April 2013}
	\begin{itemize}
		\resitem{Provide college-wide technical support in the analysis, design, programming and maintenance of administrative information systems and applications.}
		\item Write scripts to interface with Ellucian (formerly Sungard) Banner.
		\item  Report writing from Oracle databases
		\item Linux server security, updates, and maintenance
		\item Troubleshoot and update the Continuing Education website
	\end{itemize}		
	
\item
	\ressubheading{SJGC Associates}{Murrells Inlet, SC}{Software Analyst}{March 2011 - October 2011}
	\begin{itemize}
		\resitem{Configure and maintain email and web servers to support email marketing.}
		\item Migrated email servers from Windows to Linux
		\item  MS-SQL and MySQL database administration
		\item Postfix and Courier administration
		\item Software and web development
	\end{itemize}	
	
	
\item
	\ressubheading{Web Data Software, LLC}{North Myrtle Beach, SC}{Software Developer}{September 2010 - September 2011}
	\begin{itemize}
		\resitem{Software and web-based development.}
		\item Develop and interface with web services (SOAP/REST/XML-RPC)
		\item MS-SQL database administration
		\item  OAuth integration
	\end{itemize}	
	
\item
	\ressubheading{Coastal Carolina University}{Conway, SC}{Lab Assistant}{September 2010 - December 2010}
\end{itemize}


\end{document}